---
title: "mfl_basics"
author: "Tan Ho"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mfl_basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here's what a basic dynasty league analysis might look like on MFL!

```{r setup}
suppressPackageStartupMessages({
  library(ffscrapr)
  library(dplyr)
  library(tidyr)
})
```

Set up the connection to the league:

```{r}
ssb <- mfl_connect(season = 2020, league_id = 54040, rate_limit_number = 3, rate_limit_seconds = 6)
ssb
```

Cool! Let's have a deeper look at what this league is like.

```{r}

ssb_summary <- ff_league(ssb)

str(ssb_summary)
```

Okay, so it's the Smash Bros Dynasty League, it's a 1QB league with 14 teams, best ball scoring, half ppr and point-per-first-down settings. 

Let's grab the rosters now. 

```{r}
ssb_rosters <- ff_rosters(ssb)

head(ssb_rosters)
```

## Values

Cool! Let's pull in some additional context by adding DynastyProcess player values. 

```{r}

player_values <- dp_values("values-players.csv")

# The values are stored by fantasypros ID since that's where the data comes from. 
# To join it to our rosters, we'll need playerID mappings.

player_ids <- dp_playerids() %>% 
  select(mfl_id,fantasypros_id)

player_values <- player_values %>% 
  left_join(player_ids, by = c("fp_id" = "fantasypros_id")) %>% 
  select(mfl_id,ecr_1qb,ecr_pos,value_1qb)

# Drilling down to just 1QB values and IDs, we'll be joining it onto rosters and don't need the extra stuff

ssb_values <- ssb_rosters %>% 
  left_join(player_values, by = c("player_id"="mfl_id")) %>% 
  arrange(franchise_id,desc(value_1qb))

head(ssb_values)
```

Let's do some team summaries now!

```{r}

value_summary <- ssb_values %>% 
  group_by(franchise_id,franchise_name,pos) %>% 
  summarise(total_value = sum(value_1qb,na.rm = TRUE)) %>%
  ungroup() %>% 
  group_by(franchise_id,franchise_name) %>% 
  mutate(team_value = sum(total_value)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = pos, values_from = total_value) %>% 
  arrange(desc(team_value))

value_summary

```

So with that, we've got a team summary of values! I like applying some context, so let's turn these into percentages.

```{r}
value_summary_pct <- value_summary %>% 
  mutate_at(c("team_value","QB","RB","WR","TE"),~.x/sum(.x)) %>% 
  mutate_at(c("team_value","QB","RB","WR","TE"),round, 3)

value_summary_pct
```

Armed with a value summary like this, we can see team strengths and weaknesses pretty quickly, and figure out who might be interested in your positional surpluses and who might have a surplus at a position you want to look at.


## Age
Another question you might ask: what is the average age of any given team?

I like looking at average age by position, but weighted by dynasty value. This helps give a better idea of age for each team!

```{r}

age_summary <- ssb_values %>% 
  group_by(franchise_id,pos) %>% 
  mutate(position_value = sum(value_1qb,na.rm=TRUE)) %>% 
  ungroup() %>% 
  mutate(weighted_age = age*value_1qb/position_value) %>% 
  group_by(franchise_id,franchise_name,pos) %>% 
  summarise(count = n(),
            age = sum(weighted_age,na.rm = TRUE)) %>% 
  pivot_wider(names_from = pos,
              values_from = c(age,count))

age_summary

```

